Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
restructures into smaller chunks

We apply Apriori algorithm:
```{r AR apriori}

# Run the apriori algorithm with desired parameters
my_apriori <- function(data, appearance = NULL){

@@

#
# Generating asocciation rules
AR_taken <- my_apriori(transactions)

@@

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
     file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)

@@

```
We apply cspade followed by rule induction
```{r cspade and rule induction, cache = F}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}

#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )

@@

#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,

>>>>

We apply Apriori algorithm:
```{r my_apriori function}
# Run the apriori algorithm with desired parameters
my_apriori <- function(data, appearance = NULL){

@@

```{r AR apriori}

# Generating asocciation rules
AR_taken <- my_apriori(transactions)

@@

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
```

@@

```
We apply cspade followed by rule induction
```{r my_SR function}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}
```

We generate sequence rules:
```{r cspade and rule induction, cache = F}
#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )

@@

```
We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,
